Active Code Completion

### 2012-04-12 icse12/graphite-icse12.tex
Margin and font issues for ICSE12 final submission fixed.
Moved graphite URL into a footnote per publisher request.

\author{\IEEEauthorblockN{Cyrus Omar, YoungSeok Yoon, Thomas D. LaToza, Brad A. Myers}
\IEEEauthorblockA{Carnegie Mellon University, 
Pittsburgh, PA, USA\\
\small{\texttt{\{comar,youngseok,tlatoza,bam\}$@$cs.cmu.edu}}\\
\small{\texttt{\url{http://www.cs.cmu.edu/~NatProg/graphite.html}}}}
}

@@

\begin{figure*}\label{color}
\begin{center}
\includegraphics[width=\textwidth]{color_palette.png}\end{center}
\caption{(a) An example code completion palette associated with the \texttt{Color} class. (b) The source code generated by this palette.}
\end{figure*}

If the developer invokes the code completion command at the indicated cursor position (\textvisiblespace), the editor  looks  for a {\it palette definition} associated with the {\it type} of the expression being entered, which in this case is  \verb|Color|. If an associated palette is found, a menu item briefly describing this palette is added to the standard code completion menu. When selected, the corresponding palette is shown, replacing the standard code completion menu. Figure 1a gives an example of a simple palette that may be associated with the \verb|Color| class\footnote{A video demonstrating this process is available from the webpage above.}.

@@

\begin{figure}
\begin{tabular}{lccc}
 & Regular Expressions &  & SQL\\
 \hline
Separate test script & 29.6\% &  & 15.4\%\\
Guess and check & 14.0\% &  & 16.1\%\\
External tool & \textbf{37.9\%} &  & \textbf{58.6\%}\\
Search for examples & 12.3\% & & 5.1\% \\
Other & 6.2\% & & 4.9\% \\
\hline
\end{tabular}
\caption{Distribution of responses to survey questions asking about typical strategies for writing regular expressions and SQL queries.}
\label{strategies}
\end{figure}

@@

\begin{figure}\label{collections}
\begin{center}
\begin{tabular}{l|c|c|r}
Collection Class& Total & Literal & Percentage \\
\hline
\texttt{ArrayList} & 464	&	44	&	9.5\% \\
\texttt{HashMap}	& 56 & 19 & 33.9\% \\
\texttt{HashSet} & 122 & 62 & 50.8\% \\
\texttt{Hashtable} & 86 & 10 & 11.6\% \\
\texttt{Vector} & 729 & 31 & 4.2\% \\
\hline
\textbf{Total} & 1457 & 166 & 11.4\% \\
\hline
\end{tabular}
\caption{Usage patterns for common Java collection classes in the \texttt{java.util} package in our code corpus. Uses that fit a pattern that can be captured by a literal make up a significant portion of all uses. Not all possible usage scenarios of this type were captured by our analysis, so these numbers are lower bounds.}
\end{center}
\end{figure}

@@

\subsection{Palette Discovery}
\begin{figure*}\begin{center}
\vspace{2mm}
\includegraphics[scale=.6]{regex.png}\end{center}
\caption{The regular expression palette developed using Graphite and used by subjects in the treatment group of the user study described in Sec. VI.}
\end{figure*}

@@

% use section* for acknowledgement
\section*{Acknowledgment}
{We would like to thank the participants in our survey and pilot study, Jonathan Aldrich, the PLAID group, the students of 05-899D, anonymous reviewers and the UIUC Software Engineering Seminar group for valuable feedback. 
This material is based upon work supported by the National Science Foundation under Grant No. CCF-0811610. CO is supported by a DOE CSGF under Grant No. DE-FG02-97ER25308, and YY is supported by the Korea Foundation for Advanced Studies.}

>>>>

\author{\IEEEauthorblockN{Cyrus Omar, YoungSeok Yoon, Thomas D. LaToza, Brad A. Myers}
\IEEEauthorblockA{Carnegie Mellon University, 
Pittsburgh, PA, USA\\
\small{{\{comar,youngseok,tlatoza,bam\}$@$cs.cmu.edu}}\\
}}

@@

\begin{figure*}\label{color}
\begin{center}
\includegraphics[width=40pc]{color_palette.png}\end{center}
\caption{(a) An example code completion palette associated with the \texttt{Color} class. (b) The source code generated by this palette.}
\end{figure*}

If the developer invokes the code completion command at the indicated cursor position (\textvisiblespace), the editor  looks  for a {\it palette definition} associated with the {\it type} of the expression being entered, which in this case is  \verb|Color|. If an associated palette is found, a menu item briefly describing this palette is added to the standard code completion menu. When selected, the corresponding palette is shown, replacing the standard code completion menu. Figure 1a gives an example of a simple palette that may be associated with the \verb|Color| class\footnote{A video demonstrating this process is available at \\\url{http://www.cs.cmu.edu/~NatProg/graphite.html}.}.

@@

\begin{figure}
\vspace{2mm}
\begin{tabular}{lccc}
 & Regular Expressions &  & SQL\\
 \hline
Separate test script & 29.6\% &  & 15.4\%\\
Guess and check & 14.0\% &  & 16.1\%\\
External tool & \textbf{37.9\%} &  & \textbf{58.6\%}\\
Search for examples & 12.3\% & & 5.1\% \\
Other & 6.2\% & & 4.9\% \\
\hline
\end{tabular}
\caption{Distribution of responses to survey questions asking about typical strategies for writing regular expressions and SQL queries.}
\label{strategies}
\vspace{-2mm}
\end{figure}

@@

\begin{figure}\label{collections}
\vspace{2mm}
\begin{center}
\begin{tabular}{l|c|c|r}
Collection Class& Total & Literal & Percentage \\
\hline
\texttt{ArrayList} & 464	&	44	&	9.5\% \\
\texttt{HashMap}	& 56 & 19 & 33.9\% \\
\texttt{HashSet} & 122 & 62 & 50.8\% \\
\texttt{Hashtable} & 86 & 10 & 11.6\% \\
\texttt{Vector} & 729 & 31 & 4.2\% \\
\hline
\textbf{Total} & 1457 & 166 & 11.4\% \\
\hline
\end{tabular}
\caption{Usage patterns for common Java collection classes in the \texttt{java.util} package in our code corpus. Uses that fit a pattern that can be captured by a literal make up a significant portion of all uses. Not all possible usage scenarios of this type were captured by our analysis, so these numbers are lower bounds.}
\end{center}
\vspace{-2mm}
\end{figure}

@@

\subsection{Palette Discovery}
\begin{figure*}\begin{center}
\vspace{2mm}
\includegraphics[width=33pc]{regex.png}\end{center}
\caption{The regular expression palette developed using Graphite and used by subjects in the treatment group of the user study described in Sec. VI.}
\end{figure*}

@@

% use section* for acknowledgement
\section*{Acknowledgment}
{We would like to thank the participants in our survey and pilot study, Jonathan Aldrich, the PLAID group, the students of 05-899D, anonymous reviewers and the UIUC Software Engineering Seminar group for valuable feedback. 
This material is based upon work supported by the National Science Foundation under Grant No. CCF-0811610. CO is supported by a DOE CSGF under Grant No. DE-FG02-97ER25308 and NSF grant CCF-1116907, and YY is supported by the Korea Foundation for Advanced Studies.}
